Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-08-28 paper.tex

\author{
    \IEEEauthorblockN{
        Alessio Angius\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
        Danila Oleynik\IEEEauthorrefmark{1}\IEEEauthorrefmark{5},
        Sergey Panitkin\IEEEauthorrefmark{1}\IEEEauthorrefmark{4},
        Matteo Turilli\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},\\
        Kaushik De\IEEEauthorrefmark{5},
        Alexei Klimentov\IEEEauthorrefmark{4},
        Sarp H. Oral\IEEEauthorrefmark{6},
        Jack C. Wells\IEEEauthorrefmark{7} and
        Shantenu Jha\IEEEauthorrefmark{2}
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{1}First authors, alphabetical order
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{2}Department of Electric and Computer Engineering, Rutgers University, NJ, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{4}Physics Department, Brookhaven National Laboratory, NY, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{5}Physics Department, University of Texas Arlington, TX, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{6}Oak Ridge Leadership Computing Facility, Oak Ridge National Laboratory, TN, USA
        }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{7}National Center for Computational Sciences, Oak Ridge National Laboratory, TN, USA
        }
}

>>>>

\author{
    \IEEEauthorblockN{
        Alessio Angius\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
        Danila Oleynik\IEEEauthorrefmark{1}\IEEEauthorrefmark{5},
        Sergey Panitkin\IEEEauthorrefmark{1}\IEEEauthorrefmark{4},
        Matteo Turilli\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},\\
        Kaushik De\IEEEauthorrefmark{5},
        Alexei Klimentov\IEEEauthorrefmark{4},
        Sarp Oral\IEEEauthorrefmark{6},
        Jack C. Wells\IEEEauthorrefmark{7} and
        Shantenu Jha\IEEEauthorrefmark{2}
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{1}First authors, alphabetical order
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{2}Department of Electric and Computer Engineering, Rutgers University, NJ, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{4}Physics Department, Brookhaven National Laboratory, NY, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{5}Physics Department, University of Texas Arlington, TX, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{6}Oak Ridge Leadership Computing Facility, Oak Ridge National Laboratory, TN, USA
        }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{7}National Center for Computational Sciences, Oak Ridge National Laboratory, TN, USA
        }
}
